Compositional equivalences based on Open pNets

### 2020-01-31 2016-Weak-FH-Bisim/WeakBisim.tex
note page 12

%\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis... Donc le theoreme, tel qu'il est exprime, est vrai, mais inapplicable. La solution est dans le papier de PEPM, mais complique a expliquer...}
%\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
%\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le papier PEPM?}

\paragraph{Note on finite versus infinite open automata:} as
mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
automata. More precisely, in \cite{hou:hal-02406098}, we formely define
\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
and \emph{structural open automata} (finite) that can be generated as
the semantics of pNets, and used in the implementation. Then we define
an alternative version of our bisimulation, called
Structural-FH-Bisimulation, based on structural open automata, and
prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
In the sequel, all mentions of finite automata, and algorithms for
bisimulations, implicitely refer to their \emph{structural} versions.

>>>>

\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le
  papier PEPM?}
\TODO{Ludo, tu peux relire, stp ?}

\paragraph{Note on finite versus infinite open automata:} as
mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
automata. More precisely, in \cite{hou:hal-02406098}, we formely define
\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
and \emph{structural open automata} (finite) that can be generated as
the semantics of pNets (see Def. \ref{def:operationalSemantics}), and used in the implementation. Then we define
an alternative version of our bisimulation, called
structural-FH-Bisimulation, based on structural open automata, and
prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
In the sequel, all mentions of finite automata, and algorithms for
bisimulations, implicitely refer to their \emph{structural} versions.
